Covariates analysis of MSBB RNASeq data

### 2016-05-25 code/Rmd/MSSM_RNASeq_PlaqueMean.Rmd
Added markdown to process MSBB data with mean plaque adjustments

knit2synapse::knitToFolderEntity(file = "./MSSM_RNASeq.Rmd",
                                 parentId ="syn5570248",
                                 entityName = 'MSBB RNASeq')
```

@@

# library(doParallel)
# library(foreach)
# 
# cl = makeCluster(12)
# registerDoParallel(cl)

@@

thisFileName <- 'MSSM_RNASeq.Rmd'

@@

# Select covariates of interest
FactorCovariates <- c('RACE', 'SEX', 'BrainRegion.Dx', 'Batch', 'BB')
ContCovariates <- c('PMI', 'AOD', 'RIN', 'RIN2')

@@

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "MSBB RNASeq", parentId = parentId)
CODE <- synStore(CODE)

>>>>

knit2synapse::knitToFolderEntity(file = "./MSSM_RNASeq_PlaqueMean.Rmd",
                                 parentId ="syn5570248",
                                 entityName = 'MSBB RNASeq (with adjustments for mean plaque)')
```

@@

library(doParallel)
library(foreach)

cl = makeCluster(12)
registerDoParallel(cl)

@@

thisFileName <- 'MSSM_RNASeq_PlaqueMean.Rmd'

@@

# Select covariates of interest
FactorCovariates <- c('RACE', 'SEX', 'BrainRegion.Dx', 'Batch', 'BB')
ContCovariates <- c('PMI', 'AOD', 'RIN', 'RIN2', 'PlaqueMean')

@@

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "MSBB RNASeq (with adjustments for mean plaque)", parentId = parentId)
CODE <- synStore(CODE)
